Industrial, large-scale model predictive control with structured neural networks

### 2020-11-03 paper.tex
sat function.
linewidth and things.

@@

Notation. The symbols $\bbI$ and $\bbR$ are 
used to denote integers and reals respectively. 
Subscripts denote restrictions 
(e.g., $\bbR_{\geq 0}$ for nonnegative reals and 
$\bbI_{a:b}$ for integers in the 
closed interval $[a, b]$). The Euclidean norm 
is denoted by $\norm{\cdot}$. A function 
$\alpha : \bbR_{\geq 0} \rightarrow \bbR_{\geq 0}$
is of class $\mathcal{K}$ if it is continuous, zero 
at zero, and strictly increasing. This function is of class 
$\mathcal{K}_{\infty}$ if it is of class $\mathcal{K}$
and unbounded ($\alpha(s) \rightarrow \infty$ as 
$s \rightarrow \infty$). A function
$\beta : \bbR_{\geq 0} \times \bbI_{\geq 0} \rightarrow \bbR_{\geq 0}$
is of class $\mathcal{KL}$ if it is continuous,
for each $k \in \bbI_{\geq 0}$, $\beta(\cdot, k)$ is of class $\mathcal{K}$,
and for each $s \geq 0$, $\beta(s, \cdot)$ is nonincreasing
and satisfies $\textnormal{lim}_{k \rightarrow \infty} \beta(s, k) = 0$.
Given $V : X \rightarrow \bbR_{\geq 0}$ and $\tau > 0$, define 
$\textnormal{lev}_{\tau} V = \{ x \in X \mid V(x) \leq \tau \}$.
Bold symbols, e.g., $\mathbf{d}$ denote sequences, 
$d(k)$ denotes an element of $\mathbf{d}$ at time 
$k \in \bbI_{\geq 0}$, and $\mathbf{d}_i$ 
denotes the collection of elements of 
$\mathbf{d}$ for $k \in \bbI_{0:i-1}$.
Define $\norm{\norm{\mathbf{d}_i}} = 
\textnormal{max}_{k \in \bbI_{0:i-1}} \norm{d(k)}$.
For a given vector $a$, lower and upper bounds 
($\underline{a}, \overline{a}$), define the saturation function 
as $\textnormal{sat}(a, \underline{a}, \overline{a}) = 
\{ a \ \textnormal{if} \ \underline{a} \leq a \leq \overline{a}; 
\underline{a} \ \textnormal{if} \ a < \underline{a};
\overline{a} \ \textnormal{if} \ \overline{a} < a \}$.

@@

\begin{table*}[t]
    \caption{Summary of the simulation study for the
    CSTRs with a flash separator example.}   
    \begin{tabular}{ |c|c|c|c|c|c|c|c| }
        \hline
        Controller & \thead{Structured network \\ architecture} & 
        \thead{Number of \\ Parameters} & 
    \thead{Memory \\ footprint \\ (mB)} & \thead{Training \\ time \\ (min)} &
        \thead{\% Performance\\ losses \\ Expected, Unexpected \\ plant behaviors} & \thead{Average \\ speedup} & \thead{Worst case \\ speedup} \\
        \hline
    SS &  &  & &  & 85.18\%, 106.39 \% &  & \\ 
    satK &  &  &  &  & 41.03\%, 27.61 \% & $2.47 \times 10^5$ & 
    $3.07 \times 10^5$ \\ 
    SH &  &  &  &  & 1.61\%, 2.46 \% & $3.75 \times 10^3$ & $8.4 \times 10^1$ \\ 
    NN-UNS &  &  &  &  & 80.49\%, 73.29 \% & $9.31 \times 10^4$ & $4.99 \times 10^3$ \\ 
NN-3-448 & [72, 448, 448, 448, 6] & $1.10 \times 10^5$ & 0.84 & 13.02 & 0.28 \%, 5.57 \% & $5.26 \times 10^4$ & $1.45 \times 10^3$ \\ 
NN-3-480 & [72, 480, 480, 480, 6]  & $1.26 \times 10^5$ & 0.96  & 12.51 & 0.34 \%, 7.58\% & $5.09 \times 10^4$ & $1.53 \times 10^4$ \\ 
NN-3-512 & [72, 512, 512, 512, 6]  & $1.42 \times 10^5$ & 1.08  & 12.77 & 0.16 \%, 5.90 \% & $4.62 \times 10^4$ & $1.58 \times 10^4$ \\ 
        \hline
       \end{tabular}
       \label{table:cstrs}      
\end{table*}

>>>>

\newcommand{\underl}[1]{\underline{#1}}
\newcommand{\overl}[1]{\overline{#1}}
\newcommand{\satlb}[1]{\textnormal{sat}(#1, \underline{#1}, \overline{#1})}
\newcommand{\tif}{\textnormal{if}}

@@

Notation. The symbols $\bbI$ and $\bbR$ are used to denote integers and reals
respectively. Subscripts denote restrictions (e.g., $\bbR_{\geq 0}$ for
nonnegative reals and $\bbI_{a:b}$ for integers in the closed interval $[a,
b]$). The Euclidean norm is denoted by $\norm{\cdot}$. A function $\alpha :
\bbR_{\geq 0} \rightarrow \bbR_{\geq 0}$ is of class $\mathcal{K}$ if it is
continuous, zero at zero, and strictly increasing. This function is of class
$\mathcal{K}_{\infty}$ if it is of class $\mathcal{K}$ and unbounded ($\alpha(s)
\rightarrow \infty$ as $s \rightarrow \infty$). A function $\beta : \bbR_{\geq
0} \times \bbI_{\geq 0} \rightarrow \bbR_{\geq 0}$ is of class $\mathcal{KL}$ if
it is continuous, for each $k \in \bbI_{\geq 0}$, $\beta(\cdot, k)$ is of class
$\mathcal{K}$, and for each $s \geq 0$, $\beta(s, \cdot)$ is nonincreasing and
satisfies $\textnormal{lim}_{k \rightarrow \infty} \beta(s, k) = 0$. Given $V :
X \rightarrow \bbR_{\geq 0}$ and $\tau > 0$, define $\textnormal{lev}_{\tau} V =
\{ x \in X \mid V(x) \leq \tau \}$. Bold symbols, e.g., $\mathbf{d}$ denote
sequences, $d(k)$ denotes an element of $\mathbf{d}$ at time $k \in \bbI_{\geq
0}$, and $\mathbf{d}_i$ denotes the collection of elements of $\mathbf{d}$ for
$k \in \bbI_{0:i-1}$. Define $\norm{\norm{\mathbf{d}_i}} = \textnormal{max}_{k
\in \bbI_{0:i-1}} \norm{d(k)}$. For a given vector $a$, lower and upper bounds
($\underl{a}, \overl{a}$), define the saturation function as $\satlb{a} = \{ a \
\tif \ \underl{a} \leq a \leq \overl{a}; \underl{a} \ \tif \ a < \underl{a};
\overl{a} \ \tif \ \overl{a} < a \}$.

@@

\begin{table*}[t]
    \caption{Summary of the simulation study for the CSTRs with a flash
    separator example.}   
    \begin{tabular}{ |c|c|c|c|c|c|c|c| }
        \hline
        Controller & \thead{Structured network \\ architecture} & \thead{Number
        of \\ Parameters} & \thead{Memory \\ footprint \\ (mB)} &
        \thead{Training \\ time \\ (min)} & \thead{\% Performance\\ losses \\
        Expected, Unexpected \\ plant behaviors} & \thead{Average \\ speedup} &
        \thead{Worst case \\ speedup} \\
        \hline
    SS &  &  & &  & 85.18\%, 106.39 \% &  & \\ 
    satK &  &  &  &  & 41.03\%, 27.61 \% & $2.47 \times 10^5$ & $3.07 \times
    10^5$ \\ 
    SH &  &  &  &  & 1.61\%, 2.46 \% & $3.75 \times 10^3$ & $8.4 \times 10^1$ \\

    NN-UNS &  &  &  &  & 80.49\%, 73.29 \% & $9.31 \times 10^4$ & $4.99 \times
    10^3$ \\ 
NN-3-448 & [72, 448, 448, 448, 6] & $1.10 \times 10^5$ & 0.84 & 13.02 & 0.28 \%,
5.57 \% & $5.26 \times 10^4$ & $1.45 \times 10^3$ \\ 
NN-3-480 & [72, 480, 480, 480, 6]  & $1.26 \times 10^5$ & 0.96  & 12.51 & 0.34
\%, 7.58\% & $5.09 \times 10^4$ & $1.53 \times 10^4$ \\ 
NN-3-512 & [72, 512, 512, 512, 6]  & $1.42 \times 10^5$ & 1.08  & 12.77 & 0.16
\%, 5.90 \% & $4.62 \times 10^4$ & $1.58 \times 10^4$ \\ 
        \hline
       \end{tabular}
       \label{table:cstrs}      
\end{table*}
